Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
figs

We first evaluate the curvature estimation on a full-resolution
geometry obtained by disabling the LoD criterion at the mesh
generation step. We compare the approximation made to accelerate 
visualisation with the ground truth result obtained at level $l_0$.
We also compare it with the hierarchical algorithm.
The results are presented table \ref{tab:full-res-stat}, and illustrated
figure \ref{fig:refine}.

@@

For all illustrations, we use directly normal vectors computed by algorithm
discussed in Section~\ref{sec:curv-tens-estim}

\begin{table}
  \begin{center}

	\begin{tabular}{@{}lrrrrr@{}}
      \toprule
      & \multicolumn{5}{c}{$R=8$}\\
      \cmidrule(r){2-6}
    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      1468 & 2 & 28 & 260 & 2104\\
      %Time (in ms) &
      %208 & 15 & 26 & 93 & 642\\
      $L_\infty$ error (\wrt $l_0$) &
      0.051 & 0.306 & 0.085 & 0.047 & 0\\
      $L_2$ error (\wrt $l_0$) &
      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0\\
      \bottomrule
    \end{tabular}

@@

\begin{figure}[!htbp]
  \begin{center}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l3_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l2_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l1_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l0_a}}
  \end{center}
  \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
  %
  For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
  \label{fig:refine}
\end{figure}
\todo[inline]{blabla experiments}

@@

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_mean}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_gaussian}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_k1}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_k2}}\\
    {\includegraphics[height=2.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_max_zoom}}
    {\includegraphics[height=2.0cm]{figs/snow_I08iso_233_r20_l0_m3}}\\
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.
    Illustration of mean curvature computation of snow microstructures.
    %
    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}

>>>>

We first evaluate the curvature estimation on a full-resolution
geometry obtained by disabling the LoD criterion at the mesh
generation step. We compare the approximation made to accelerate
visualisation with the ground truth result obtained at level $l_0$.
We also compare it with the hierarchical algorithm.
The results are presented table \ref{tab:full-res-stat}, and illustrated
figure \ref{fig:refine}. For all illustrations, we use directly normal vectors computed by algorithm
discussed in Section~\ref{sec:curv-tens-estim}

@@

\begin{table}
  \begin{center}
	\begin{tabular}{@{}lrrrrr@{}}
      \toprule
      & \multicolumn{5}{c}{$R=8$}\\
      \cmidrule(r){2-6}
    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
      \midrule
      Number of texture fetches &
      1468 & 2 & 28 & 260 & 2104\\
      %Time (in ms) &
      %208 & 15 & 26 & 93 & 642\\
      $L_\infty$ error (\wrt $l_0$) &
      0.051 & 0.306 & 0.085 & 0.047 & 0\\
      $L_2$ error (\wrt $l_0$) &
      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0\\
      \bottomrule
    \end{tabular}

@@

\begin{figure}[!htbp]
  \begin{center}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l3_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l2_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l1_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l0_a}}
  \end{center}
  \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).}
  \label{fig:refine}
\end{figure}
\todo[inline]{blabla experiments}

@@

\begin{figure}
  \begin{center}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_mean}}
    {\includegraphics[width=2.7cm]{figs/EG_dragon_gaussian}}
    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_min_zoom}}
    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_max_zoom}}\\
    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
    {\includegraphics[height=4.0cm]{figs/xyzrgb_dragon-510_R8_mean}}
    {\includegraphics[height=3.5cm]{figs/snow_I08iso_233_r20_l0_m3}}\\
    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
  \end{center}
  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
    objets.. + dynamique.
    Illustration of mean curvature computation of snow microstructures.
    %
    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
  \label{fig:full}
\end{figure}
